Structuring College Access

### 2025-04-16 index.qmd
update la_segment_map.png

- Racial inequity results from:
  - College Board student list databases exclude non-test-takers
  - Test scores and geographic filters compound disparities in excluded prospects
    - [SAT scores + Segment, LA map](#){data-modal-type="image" data-modal-url="assets/images/la_segment_map.png"}
    - CRYSTAL -- REPLACE W/ STATIC MAP THAT JUST HAS LA
- Collge Board creates new geographic filters that include/exclude ([FIGURE](#){data-modal-type="image" data-modal-url="assets/images/research_univ_list_filters.png"})

>>>>

- Racial inequity results from:
  - College Board student list databases exclude non-test-takers
  - Test scores and geographic filters compound disparities in excluded prospects
    - [SAT scores + Segment, LA map](#){data-modal-type="image" data-modal-url="assets/images/la_segment_map.png"}
- Collge Board creates new geographic filters that include/exclude ([FIGURE](#){data-modal-type="image" data-modal-url="assets/images/research_univ_list_filters.png"})
